A word-sense representation for documents based on information value and word sense disambiguation

### 2014-03-22 paper/results.tex
some improvements on tables
add captions to tables
remove everything but page number from footer

\begin{tabular}{p{1.1cm} p{1.1cm} p{1.1cm} p{1.5cm} p{1.5cm}}
        \toprule
        Work 1 & Work 2 & Work 3 & Work 4 & Work 5 \\
%        \multicolumn{2}{c}{Work 1} & \multicolumn{2}{c}{Work 2} & \multicolumn{2}{c}{Work 3} & \multicolumn{2}{c}{Work 4} & \multicolumn{2}{c}{Work 5} \\
        \midrule
        marx & enterprise & physics & local\_anesthetic & rent \\
        revolution & depository\_financial\_institution & sociable & organization  & land \\
        plant & imperialism & space & marriage & peasant \\
        engels & universe & time  & criticism & capital \\
        club & million & berkeley & revolutionist & revolution \\
        power & colony & truth & freedom & marx \\
        party & colonial &  aim & newspaper & people \\
        sociable &  product & sensation & worker & nationalization \\
        experience & penny & experience & consciousness & restoration \\
        bernstein & company  & engels & newspaper & right \\
        question & capitalist & motion & businessperson & private  \\
        equality & monopoly & marx & mass & farming \\
        phase & area &  book & motion & free \\
        commune & policy &  plant & german  & central \\
        one &  power & general & goverment & land \\
        democracy & banks &  helmholtz & political\_orientation & capitalism \\
        class &  worker & neccesity & party & democracy \\
        law &  imperialist & law & secret & landlord \\
        communism & company & sensation & working & farming \\
        peer & boards & energy & class & agency \\
        \bottomrule
    \end{tabular}
\newline
%aWork1 : The State and Revolution
%work2: Lenin: Imperialism, the Highest Stage of Capitalism
%Work3: Lenin: MATERIALISM and EMPIRIO-CRITICISM
%Work4: Lenin: What Is To Be Done?
%wotk5: Lenin: The Agrarian Programme of Social-Democracy in the First Russian Revolution, 1905-1907

    \begin{tabular}{ p{2cm} p{2cm} p{3cm}}
    \toprule
    Text &  Top Sense & Sense Detected \\
    \midrule
The Agrarian Programme & marx & United States comedian; one of four brothers who made motion pictures together (1901-1979) \\
    \midrule
The State and Revolution & bernstein & United States conductor and composer (1918-1990) \\
    \bottomrule
\end{tabular}

\input{top_senses_definitions}

>>>>

\begin{table*}[ht]
\caption*{Top sense for all Lenin works}
\centering
\begin{tabular}{p{3cm} p{3cm} p{3cm} p{3cm} p{3cm}}
        \toprule
        The State and Revolution & Imperialism,the Highest .. & Materialism and ... & What Is To Be Done? &  The Agrarian Programme ... \\
%        \multicolumn{2}{c}{Work 1} & \multicolumn{2}{c}{Work 2} & \multicolumn{2}{c}{Work 3} & \multicolumn{2}{c}{Work 4} & \multicolumn{2}{c}{Work 5} \\
        \midrule
        marx & enterprise & physics & local\_anesthetic & rent \\
        revolution & depository\_financial\_institution & sociable & organization  & land \\
        plant & imperialism & space & marriage & peasant \\
        engels & universe & time  & criticism & capital \\
        club & million & berkeley & revolutionist & revolution \\
        power & colony & truth & freedom & marx \\
        party & colonial &  aim & newspaper & people \\
        sociable &  product & sensation & worker & nationalization \\
        experience & penny & experience & consciousness & restoration \\
        bernstein & company  & engels & newspaper & right \\
        question & capitalist & motion & businessperson & private  \\
        equality & monopoly & marx & mass & farming \\
        phase & area &  book & motion & free \\
        commune & policy &  plant & german  & central \\
        one &  power & general & goverment & land \\
        democracy & banks &  helmholtz & political\_orientation & capitalism \\
        class &  worker & neccesity & party & democracy \\
        law &  imperialist & law & secret & landlord \\
        communism & company & sensation & working & farming \\
        peer & boards & energy & class & agency \\
        \bottomrule
        \multicolumn{5}{p{\linewidth}}{The table shows $top-senses$ obtained from the choosen works. Each $top-sense$ is ordered according to the information value score that we obtained previous to apply the $WSD$ algorithm. Most of the senses found by our algorithm were the senses related to the works, except for some of them. On Whats is to be done? local\_anesthetic was matched as sense. On State and revolution Marx was matched with a United States comedian and the same result we got with Berstein that was matched with a composer} \\
    \end{tabular}
\end{table*}

### 2014-03-22 paper/top_senses_definitions.tex
add captions to tables
remove everything but page number from footer

\begin{table*}[ht]
\caption{Top 5 Senses with Closest Handpicked Synset}
\centering
\begin{tabular}{ p{2.5cm} p{9cm} p{2.5cm}}
    \toprule
    Synset & Gloss  & Handpicked \cr
    \hline
    \midrule  \multicolumn{3}{c}{The State and Revolution} \\  \midrule
    revolution.n.01 & a drastic and far-reaching change in ways of thinking and behaving & revolution.n.01\\
    imperialism.n.02 & a political orientation that advocates imperial interests & communism.n.02\\
    proletarian.n.01 & a member of the working class (not necessarily employed) & peer.n.01\\
    war.n.01 & the waging of armed conflict against an enemy & experience.n.03\\
    practice.n.03 & translating an idea into action & experience.n.03\\
    \midrule  \multicolumn{3}{c}{Lenin: Imperialism, the Highest Stage of Capitalism} \\  \midrule
    proletarian.n.01 & a member of the working class (not necessarily employed) & capitalist.n.02\\
    hair.n.01 & a covering for the body (or parts of it) consisting of a dense growth of threadlike structures (as on the human head); helps to prevent heat loss & universe.n.01\\
    money.n.01 & the most common medium of exchange; functions as legal tender & penny.n.02\\
    practice.n.03 & translating an idea into action & monopoly.n.01\\
    toilet.n.04 & the act of dressing and preparing yourself & monopoly.n.01\\
    \midrule  \multicolumn{3}{c}{Lenin: MATERIALISM and EMPIRIO-CRITICISM} \\  \midrule
    revolution.n.01 & a drastic and far-reaching change in ways of thinking and behaving & experience.n.03\\
    proletarian.n.01 & a member of the working class (not necessarily employed) & helmholtz.n.01\\
    philosophy.n.02 & the rational investigation of questions about existence and knowledge and ethics & physics.n.01\\
    war.n.01 & the waging of armed conflict against an enemy & experience.n.03\\
    strategy.n.02 & the branch of military science dealing with military command and the planning and conduct of a war & physics.n.01\\
    \midrule  \multicolumn{3}{c}{Lenin: What Is To Be Done?} \\  \midrule
    imperialism.n.02 & a political orientation that advocates imperial interests & political\_orientation.n.01\\
    proletarian.n.01 & a member of the working class (not necessarily employed) & worker.n.01\\
    practice.n.03 & translating an idea into action & motion.n.03\\
    money.n.01 & the most common medium of exchange; functions as legal tender & mass.n.01\\
    war.n.01 & the waging of armed conflict against an enemy & motion.n.03\\

@@

    \bottomrule
\end{tabular}
\end{table*}

>>>>

\begin{table*}[ht]
    \caption*{Top 5 Senses with Closest Handpicked Synset (Path Distance)}
\centering
\begin{tabular}{ p{2.5cm} p{9cm} p{2.5cm}}
    \toprule
    Synset & Gloss  & Handpicked \cr
    \hline
    \midrule  \multicolumn{3}{c}{The State and Revolution} \\  \midrule
    revolution.n.01 & a drastic and far-reaching change in ways of thinking and behaving & revolution.n.01\\
    imperialism.n.02 & a political orientation that advocates imperial interests & communism.n.02\\
    proletarian.n.01 & a member of the working class (not necessarily employed) & peer.n.01\\
    war.n.01 & the waging of armed conflict against an enemy & experience.n.03\\
    practice.n.03 & translating an idea into action & experience.n.03\\
    \midrule  \multicolumn{3}{c}{Lenin: Imperialism, the Highest Stage of Capitalism} \\  \midrule
    proletarian.n.01 & a member of the working class (not necessarily employed) & capitalist.n.02\\
    hair.n.01 & a covering for the body (or parts of it) consisting of a dense growth of threadlike structures (as on the human head); helps to prevent heat loss & universe.n.01\\
    money.n.01 & the most common medium of exchange; functions as legal tender & penny.n.02\\
    practice.n.03 & translating an idea into action & monopoly.n.01\\
    toilet.n.04 & the act of dressing and preparing yourself & monopoly.n.01\\
    \midrule  \multicolumn{3}{c}{Lenin: MATERIALISM and EMPIRIO-CRITICISM} \\  \midrule
    revolution.n.01 & a drastic and far-reaching change in ways of thinking and behaving & experience.n.03\\
    proletarian.n.01 & a member of the working class (not necessarily employed) & helmholtz.n.01\\
    philosophy.n.02 & the rational investigation of questions about existence and knowledge and ethics & physics.n.01\\
    war.n.01 & the waging of armed conflict against an enemy & experience.n.03\\
    strategy.n.02 & the branch of military science dealing with military command and the planning and conduct of a war & physics.n.01\\
    \midrule  \multicolumn{3}{c}{Lenin: What Is To Be Done?} \\  \midrule
    imperialism.n.02 & a political orientation that advocates imperial interests & political\_orientation.n.01\\
    proletarian.n.01 & a member of the working class (not necessarily employed) & worker.n.01\\
    practice.n.03 & translating an idea into action & motion.n.03\\
    money.n.01 & the most common medium of exchange; functions as legal tender & mass.n.01\\
    war.n.01 & the waging of armed conflict against an enemy & motion.n.03\\

@@

    \bottomrule
    \multicolumn{3}{p{\linewidth}}{Top-senses for each work are shown on the first column. The gloss that our algorithm calculated is on the second column. Third column shows the closest handpicked sense using path distance. On imperialism notice the appareance of hair.n.01 and the matched sense universe.n.01. On Materialism and Empirio-criticism first sense was matched with experience.n.03. Note that many synsets were close to law.n.04 (TODO: necesito mostrar esto en la tabla usando los top7 creo)} \\
\end{tabular}
\end{table*}
